### 2014-03-18 HowtoHowtoCapon/submission/submit1/answer/answer.tex
la2pdf commit - 2014:03:18	11:33:08	(Tue18.Mar)

\ai{Yes, we are pre-steering the array for every angle. We will attempt to clarify this further, and add a remark saying that while not necessary here we could have phase steered the array by introducing the steering vector $\vec s$.}

@@

\ai{Again, thank you for a helpful remark, we will clarify this as well. After pulse compressing a chirp using the full transceiver bandwidth (30~kHz) range resolution is roughly $\Delta r \approx \frac{1}{B} = 2.5$~cm, which corresponds to a sample shift of $\Delta n = \frac{\Delta r f_s}{c} = 0.6$. Hence we cover the entire pulse compressed signal with only a few samples. $K=2$ corresponds to a window length of $2K+1=5$ samples, as is shown by (4) in the article.} 

>>>>

\ai{Yes, we are pre-steering the array for every angle. We have clarified this further (see 3.), and added a remark saying that while not necessary here we could have phase steered the array by introducing the steering vector $\vec s$.}

@@

\ai{Again, thank you for a helpful remark, we will clarify this as well. After pulse compressing a chirp using the full transceiver bandwidth (30~kHz) range resolution is roughly $\Delta r \approx \frac{1}{B} = 2.5$~cm, which corresponds to a sample shift of just 1.2\footnote{$\Delta n = \frac{\Delta r f_s}{c} = 1.2$}. Hence we cover the entire pulse compressed signal with only a few samples. $K=2$ corresponds to a window length of $2K+1=5$ samples, as is shown by (4) in the article.} 
